\Large Generative Dynamics of Supreme Court Citations: \\ Analysis with a New Statistical Model

### 2020-04-30 Tex/paper.tex
revised covariate terms

Covariate effects are accounted for in the c-ERGM via the term that is used to specify the effect of covariates in other ERGM family models, as
$$h_{covariate}(C_t,C_{<t},X) =  \sum_{ij} C_{ij,t}X_{ij}.$$ Since $C_{ij,t}$ is a binary indicator of whether case $i$ cites case $j$, $h_{covariate}$ amounts to the sum of covariate values among directed dyads for which we observed a citation. The dyadic interpretation of the coefficient attributed to this term is the change in the log odds of a tie from $i$ to $j$ given a unit increase in $X_{ij}$ (i.e., exactly the interpretation of the effect of a covariate in logistic regression). We include several exogenous covariates based on this standard statistic formulation.

The first covariate (i.e., $X$) we incorporate into the model accounts for the degree to which cases cite those that are similar in terms of the ideological positions of the justices who supported the decision. We account for this effect following \citet{spriggs2001explaining}, who find that cases are more likely to be overruled when the Court is ideologically distant from the median justice in the majority coalition that decided the case. \citet{clark2010locating} estimates a latent coordinate model of Supreme Court opinions based on the network of case-to-case citations. They find that the majority opinion falls at the ideal point of the median member of the majority coalition in the case. We include a covariate term in which $X_{ij}$ is the absolute difference between the Martin-Quinn scores \citep{martin2002dynamic} of the median justices in the majority coalitions for cases $i$ and $j$. We expect this variable to have a negative effect, which would correspond to cases citing those to which they are ideologically similar.%WE COULD USE THIS DATASET AS A SECOND APPLICATION

>>>>

Covariate effects are accounted for in the c-ERGM via the term that is used to specify the effect of covariates in other ERGM family models, as
$$h_{covariate}(C_t,C_{<t},X) =  \sum_{ij} C_{ij,t}X_{ij}.$$ Since $C_{ij,t}$ is a binary indicator of whether case $i$ cites case $j$, $h_{covariate}$ amounts to the sum of covariate values among directed dyads for which we observed a citation. The dyadic interpretation of the coefficient attributed to this term is the change in the log odds of a tie from $i$ to $j$ given a one-unit increase in $X_{ij}$ (i.e., exactly the interpretation of the effect of a covariate in logistic regression). We include several exogenous covariates based on this standard formulation.

The first covariate we incorporate into the model accounts for the degree to which cases cite those that are similar in terms of the ideological positions of the justices who supported the decision. We account for this effect following \citet{spriggs2001explaining}, who find that cases are more likely to be overruled when the Court is ideologically distant from the median justice in the majority coalition that decided the case. \citet{clark2010locating} estimates a latent coordinate model of Supreme Court opinions based on the network of case-to-case citations. They find that the majority opinion falls at the ideal point of the median member of the majority coalition in the case. We include a covariate term in which $X_{ij}$ is the absolute difference between the Martin-Quinn scores \citep{martin2002dynamic} of the median justices in the majority coalitions for cases $i$ and $j$. We expect this variable to have a negative effect, which would correspond to cases citing those to which they are ideologically similar. In addition to the absolute difference variable, we also include a linear effect of the Martin-Quinn score of the median justice in the majority coalition for case $j$, which adjusts for constant ideological biases exhibited within a given term. %WE COULD USE THIS DATASET AS A SECOND APPLICATION
